Shaping the Perception of a Robot as a Human-Like Agent by Cognitive Priming

### 2015-11-03 main.tex
WIP on the hypotheses

The study has been designed out of the following intuition: \emph{the more we
ascribe cognitive capabilities to an agent, the more we focus on its head when
interacting with it}. Eye-tracking is a natural methodology to investigate
this intuition. We hence design audio-visual stimuli that elicit different
levels of cognitive ascription onto the robot while being identical in every
other way.

We actually build several hypotheses: our baseline hypothesis \h{1} is that we
can actually create such stimuli that induce recognisable \emph{shallow} or
\emph{deeper} cognitive ascriptions onto the robot (manipulation check); and
further that these different levels of cognitive ascriptions are interpreted by
the participants as being respectively \emph{machine-like} (low level of
anthropomorphic attributions) or \emph{human-like} (higher level of
anthropomorphic attributions).

Secondly, we hypothesize (\h{2}) that the \emph{difference} of gaze
behaviours between the human and robot conditions correlates with the
participants' initial tendency to anthropomorphize, measured from a standard
pre-questionnaire: we expect that people with high tendency to anthropomorphize
will tend to have smaller differences in their gaze behaviours while watching
either a robot or a human performing the same task: if this can be observed, it
would also show that anthropomorphic attributions are related to gaze patterns.

Then, we hypothesize (\h{3}) that the gaze fixations on the head are
significantly different depending on the cognitive priming, and that a deeper
cognitive priming corresponds to longer gaze fixations on the head. This would
in turn interpreted at \emph{gaze fixations on the head is a proxy for the level
of human-likeness attribution}, and constitutes the core hypothesis of this
article.

Finally, the hypothesis \h{4} examines whether the cognitive priming affects the
general tendency to anthropomorphize, \ie whether observing \emph{one}
robot acting in an \emph{human-like} context leads to an increased level of
anthropomorphic attributions to robots \emph{in general}. This also provides us
with a way to triangulate the behavioural measures with the subjective
attribution of anthropomorphism: if such an effect is found, we can also
conclude that the cognitive priming impacts on the attribution of human-likeness,
and this, in turns, supports the hypothesis \h{3} that head fixations would
reflect not only the cognitive context of the interaction but also the level of
anthropomorphic attributions.

Figure~\ref{hyps} illustrate how these four hypotheses relate to \emph{a)}
cognitive priming, \emph{b)} anthropomorphic attributions, and \emph{c)} gaze
patterns.

\begin{figure}[ht]
\centering

\resizebox{0.5\linewidth}{!}{%

\begin{tikzpicture}[
    >=latex,
    every edge/.style={->,draw, very thick},
    every node/.style={draw, circle, text centered, text width=2.7cm}]

    \node at (0,0) (ctxt) {cognitive priming};
    \node at (-3,-3) (anthro) {Anthropomorphic attributions};
    \node at (3,-3)[circle split, text width=2.5cm] (gaze) {\textit{\small Fixations \\on head} \nodepart{lower} \textit{\small Gaze
distribution \\differences}};
    \node [draw=none,anchor=east,left=-0.5cm of gaze.west] (gazecap) {\large Gaze:};

    \path[every node/.style={draw=none}]
            (ctxt) edge [bend right] node[left] {\h{1}, \h{4}} (anthro)
            (ctxt) edge [bend left] node[right] {\h{3}} (gaze.north)
            (anthro) edge [bend right] node[above] {\h{2}} (gaze.south);
\end{tikzpicture}
}

\caption{Hypotheses of interactions between the three main concepts studied in
the article. Arrows mean ``A impacts B''.}

    \label{hyps}
\end{figure}

>>>>

\begin{inparaenum}[\itshape a\upshape)]
Two nested research questions have been presented so far: \item can we
characterize the link between expectations regarding the cognitive
skills of a robot and the effective ascription of anthropomorphic features to
this robot; and \item to this end, can we develop and validate a behavioural and
\emph{in-the-moment} metric of anthropomorphism?  \end{inparaenum}

These two questions translate into several experimental hypotheses, whose design
was guided by the following intuition: \emph{the more we ascribe cognitive
capabilities to an agent, the more likely we are to focus on its head when
interacting with it}, which suggests an eye-tracking-based investigation.

%Eye-tracking-based technique logically follows as an investigation mean, is a natural
%methodology to investigate this intuition. We hence design audio-visual stimuli
%that elicit different levels of cognitive ascription onto the robot while being
%identical in every other way.

Our baseline hypothesis \h{1} is that cognitive priming allows us to effectively create
stimuli that induce \emph{shallow} or \emph{higher} expectations regarding the
cognitive skills of the robot. This hypothesis is to be tested by asking
participants to rate the interactions depicted by the stimuli as being more
\emph{machine-like} (low ascription of cognitive skills) or \emph{human-like}
(higher expectation of cognitive competency).

Secondly, we hypothesize that people with a higher tendency to anthropomorphize
robots will tend to look at robots and humans in similar ways, contrary to
people with a lower tendency to anthropomorphize (\h{2}). If this is verified,
it supports the idea that anthropomorphic attributions affect gaze patterns. The
hypothesis can be tested by correlating the participants' tendency to
anthropomorphize, measured from a standard questionnaire, with the comparative
gazing behaviour in two conditions (human task \vs robot task).

Third, we hypothesize that in the \emph{human-like} condition (higher ascription
of cognitive skills to the robot), the participants' gaze will be directed
significantly more towards the head of the robot than in the \emph{machine-like}
condition (low ascription of cognitive skills) (\h{3}). If verified, it
effectively means that the expectations held by the participants regarding the
cognitive capabilities of the robot are reflected by the eye fixations on the
head of the robot.  The hypothesis can be tested by comparing gaze fixations in
the two conditions (\emph{human-like} \vs \emph{machine-like}).

Finally, the hypothesis \h{4} proposes that manipulating cognitive expectations
affects the broader tendency to anthropomorphize robots, \ie whether observing one
robot acting in an \emph{human-like} context leads to an increased level of
anthropomorphic attributions to robots in general. The hypothesis can be
tested by looking at pre- and post-experiment self-reports on the tendency to
anthropomorphize.

If all these hypotheses are verified, the findings can be summarized as follow:
\h{1} shows that our manipulation (based on cognitive priming) does effectively
elicit lower or higher expectations in terms of the cognitive capabilities of
the robot; \h{4} shows that these expectations influence our tendency to
anthropomorphize robots; in parallel, \h{3} shows that these same expectations
shape the way we look at the robot by eliciting specific eye fixations on the
head of the robot; finally, \h{2} suggests that the fixation on the head
reflects human-likeliness and supports the thesis that head fixation can be used
as a behavioural measure of anthropomorphism.

%Figure~\ref{hyps} illustrate how these four hypotheses relate to \emph{a)}
%cognitive priming, \emph{b)} anthropomorphic attributions, and \emph{c)} gaze
%patterns.
%
%\begin{figure}[ht]
%\centering
%
%\resizebox{0.5\linewidth}{!}{%
%
%\begin{tikzpicture}[
%    >=latex,
%    every edge/.style={->,draw, very thick},
%    every node/.style={draw, circle, text centered, text width=2.7cm}]
%
%    \node at (0,0) (ctxt) {cognitive priming};
%    \node at (-3,-3) (anthro) {Anthropomorphic attributions};
%    \node at (3,-3)[circle split, text width=2.5cm] (gaze) {\textit{\small Fixations \\on head} \nodepart{lower} \textit{\small Gaze
%distribution \\differences}};
%    \node [draw=none,anchor=east,left=-0.5cm of gaze.west] (gazecap) {\large Gaze:};
%
%    \path[every node/.style={draw=none}]
%            (ctxt) edge [bend right] node[left] {\h{1}, \h{4}} (anthro)
%            (ctxt) edge [bend left] node[right] {\h{3}} (gaze.north)
%            (anthro) edge [bend right] node[above] {\h{2}} (gaze.south);
%\end{tikzpicture}
%}
%
%\caption{Hypotheses of interactions between the three main concepts studied in
%the article. Arrows mean ``A impacts B''.}
%
%    \label{hyps}
%\end{figure}
